### 2021-09-09 input/experiments.tex
spacing, and slight work on last efb paragraph

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
around $500$ ms due to the high latency inter-continental link. The
first plateau corresponds to the source's autonomous system
acknowledging this source, while the second plateau corresponds to the
other autonomous system catching up.  The inter-continental link acts
as a bottleneck that does not exist when each cluster has its own
source.

>>>>

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
around $500$ ms due to the high latency inter-continental link. The
first plateau shows the source's autonomous system acknowledging this
source, while the second shows the other autonomous system catching
up.  The inter-continental link is a bottleneck that does not exist
when each cluster has its own source.

### 2021-09-09 input/proposal.tex
spacing, and slight work on last efb paragraph

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    upon receipt of such $\alpha_y$, either the \process already 
    \TODO{tododododotododoo.}

    ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
    S(\alpha_y)$)

    eventually every \process only delivers and forwards up-to-date
    messages, or no message at all ($\eventually d_c(m') \implies \neg
    S(m')$).

    , every \process eventually delivers and forwards the best
    up-to-date delivered messages as in Theorem~\ref{theo:bef}.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together.
\end{proof}

@@

As stated in Theorem~\ref{theo:dcp}, every \process must purge stale
messages.  To identify staleness, each \process maintains a vector of
versions that associates the respective known local counter of each
known source, or has-been source. Its size increases linearly with the
number of sources that the \process has ever known, which is the
number of \processes in the system $\mathcal{O}(V)$ in the worst case.
Nevertheless, following the principles of scoped broadcast, we expect
that every \process only acknowledges a small subset of sources.
Using such a vector, every message $m$ carries its source $s$ along
with its version $c$ that we subscript $m_{s, c}$.  Each \process
delivers and forwards
\begin{inparaenum}[(i)]
\item only newest messages (see Line~\ref{line:ascast_version}) that
\item improve their best known partition (see
  Line~\ref{line:ascast_better}).
\end{inparaenum}
This vector of versions constitutes a summary of local deliveries. It
allows a \process to detect inconsistencies in message delivery: the
parent delivered a stale message (see Line~\ref{line:ascast_version}),
or the parent delivered a worse message (see
Line~\ref{line:detectA}). This may happen in stage II of
Figure~\ref{fig:proofB} between $b$ and $c$.

>>>>

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
    eventually deliver and forward their best up-to-date message.

    %% upon receipt of such $\alpha_y$, either the \process already
    %% delivered its removal and it does

    %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
    %% S(\alpha_y)$)

    %% eventually every \process only delivers and forwards up-to-date
    %% messages, or no message at all

    %% , every \process eventually delivers and forwards the best
    %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.

    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together
  even under dynamic partitioning settings where \nodes can
  \texttt{Add} and \texttt{Del}ete their partition.
\end{proof}

@@

As stated in Theorem~\ref{theo:dcp}, every \process must purge stale
messages.  To identify staleness, each \process maintains a vector of
versions that associates the respective known local counter of each
known source, or has-been source. Its size increases linearly with the
number of sources that the \process has ever known, which is the
number of \processes in the system $\mathcal{O}(V)$ in the worst case.
Nevertheless, following the principles of scoped broadcast, we expect
that every \process only acknowledges a small subset of sources.
Using such a vector, every message $m$ carries its source $s$ along
with its version $c$ that we subscript $m_{s, c}$.  Each \process
delivers and forwards
\begin{inparaenum}[(i)]
\item only newest messages (see Line~\ref{line:ascast_version}) that
\item improve their best known partition (see
  Line~\ref{line:ascast_better}).
\end{inparaenum}
This vector of versions constitutes a summary of local deliveries. It
allows a \process to detect inconsistencies in message delivery: the
parent delivered a stale message (see Line~\ref{line:ascast_version}),
or the parent delivered a worse message (see
Line~\ref{line:detectA}). % This may happen in stage II of
% Figure~\ref{fig:proofB} between $b$ and $c$.

### 2021-09-09 input/related_work.tex
spacing, and slight work on last efb paragraph

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
  coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location, and then
\item request the actual content from possibly far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.

>>>>

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
  coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location, and then
\item request the actual content from possibly far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
Hash values are keys to retrieve the associated content location.
Before downloading any content, a \node requests its location using
its key. After round-trips between possibly distant DHT servers, the
\node gets available replicas. Contrarily to \NAME, such services do
not ensure to include the closest replica.
